Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-07-11 kappa.tex
Remove lineno, correct biblio and add DOI links.
Add figures in results summary.

% Base class and packages
\documentclass{article}
\usepackage{amsmath}
\usepackage{bm}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\usepackage{natbib}
\usepackage[onehalfspacing]{setspace}
\usepackage{physics}
\usepackage[colorlinks, citecolor=blue]{hyperref}
\usepackage[sort]{cleveref}  % needs to be loaded after hyperref
\usepackage{graphicx}
\graphicspath{{figures/}}

@@

\maketitle
\linenumbers
\tableofcontents

@@

% ----------------------------------------------------------------------
\subsection{Constant-climate runs}
% ----------------------------------------------------------------------
\todo{Figure. 3km last glacial maximum poster run?}

% ----------------------------------------------------------------------
\subsection{Daily temperature variability}
% ----------------------------------------------------------------------
\todo{Figure. Sigma distribution map}\\
\todo{Figure. Sigma effect on Cordillera runs}

% ----------------------------------------------------------------------
\subsection{Transient-climate runs}
% ----------------------------------------------------------------------
\todo{Figure. Deglaciation streamplot}\\
\todo{Figure. Cumulative ice displacement map}

>>>>

% Base class and packages
\documentclass{article}
\usepackage{amsmath}
\usepackage{bm}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage[onehalfspacing]{setspace}
\usepackage{physics}
\usepackage[colorlinks, citecolor=blue]{hyperref}
\usepackage[sort]{cleveref}  % needs to be loaded after hyperref
\usepackage{doi}  % needs to be loaded after hyperref
\usepackage{graphicx}
\graphicspath{{figures/}}

@@

\maketitle
\tableofcontents

@@

% ----------------------------------------------------------------------
\subsection{Constant-climate runs}
% ----------------------------------------------------------------------

\begin{figure*}
  \centering
  \vspace{-16mm}
  \makebox[0pt]{
  \begin{minipage}[t]{112.5mm}\vspace{0pt}
    \includegraphics{plot-lgm}
  \end{minipage}
  \hspace{1cm}
  \begin{minipage}[t]{47.5mm}\vspace{0pt}
    \caption{Constant-climate simulation of the LGM Cordilleran ice sheet using
             an horizontal resolution of 3\,km. Modelled basal topography,
             cold-based areas (hatches), surface topography (100\,m contours)
             and surface velocities. The simulation is forced by atmospheric
             fields from the NARR \citep{Mesinger.etal.2006} and a temperature
             depression of 7\,\degC, using the set-up described in \CCLI. There
             are several issues with this run. First, all east-facing margins
             are too extensive as compared to available reconstructions.
             Second, marine advance on the Pacific Shelf is too restrictive,
             most notably in the south-western corner where the Puget and Juan
             de Fuca lobes are missing. Third, en-glacial temperatures are
             anomalously low due to brutal application of cold climate
             condition to ice-free bedrock at the inception of the run.
             \todo{Add black frame, and maybe the LGM outline from Dyke?}}
  \end{minipage}
  }
  \vspace{-16mm}
  \label{fig:plot-lgm}
\end{figure*}

% ----------------------------------------------------------------------
\subsection{Daily temperature variability}
% ----------------------------------------------------------------------

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{plot-sdmap}}
  \caption{July, daily temperature variability in the Arctic, as shown by
           monthly standard deviation of near-surface daily mean air
           temperature computed from ERA-40 reanalysis
           \citep{Uppala.etal.2005}. Note the strong differences between
           continental and maritime regions, notably within the model domain
           (black rectangle). Although daily variability is lowest in summer,
           this is when it most importantly contributes to surface melt.}
  \label{fig:plot-sdmap}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{plot-sdeffect}}
  \caption{Effect of temperature variability on Cordilleran ice sheet
           simulations. Modelled basal topography and surface topography
           (250\,m contours). The simulations use atmospheric forcing from the
           NARR \citep{Mesinger.etal.2006}, a temperature depression of
           7\,\degC, and different treatments of temperature variability
           including
           \textbf{(a)} no daily variability, $\sigma=0$;
           \textbf{(b)} a constant, mean summer (JJA), model domain-averaged 
           standard deviation value, $\sigma=3.09$\,K;
           \textbf{(c)} monthly standard deviation grids derived from the NARR
           and
           \textbf{(d)} monthly grids for ice-free terrain and the
           Greenland ice sheet, ERA-40-based \citep{Uppala.etal.2005}
           parametrisation in \PSDP, ${\sigma=-0.15\cdot{T_m}+1.66}$.
           Differences in surface elevation are displayed relative to case (c).
           Note the different colour scales.}
  \label{fig:plot-sdeffect}
\end{figure}

% ----------------------------------------------------------------------
\subsection{Transient-climate runs}
% ----------------------------------------------------------------------

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{plot-snapshots}}
  \caption{\textbf{(a)} Modelled growth and decay of the last Cordilleran ice
           sheet. Basal topography surface topography (1\,km contours) and
           surface velocity (m/a).
           \textbf{(b)} Evolution of total ice volume during the entire last
           glacial cycle, expressed as meters of sea-level equivalent. The
           simulation uses a horizontal resolution of 6\,km and is forced by
           atmospheric fields from the NARR \citep{Mesinger.etal.2006} and
           temperature offset time-series derived from the GRIP
           \citep{Dansgaard.etal.1993} ice-core record as described in \CCYC.
           \todo{X-tick snapshot times on time series plot and thicken the
                 vertical lines. Add (a) and (b) subfigure labels. Link lower
                 and upper panels; see recipe at
                 \url{http://stackoverflow.com/questions/17543359/}.}}
  \label{fig:plot-snapshots}
\end{figure}
